Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-26 papers/BON_VHDL/paper.tex
added minor text

\subsection{Seamlessness and Reversibility}
\label{subsec:seamrever}
\emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
\emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code. Keeping in sync various models, documetation
and specification from forward progress to backward and redesign, preclude 
that design and implementation diverge to an inconsistent state. 
\emph{Seamlessness} also plays an important role in relating behaviours at
different levels of abstraction. For example, one may wish to analyze
a "real capacitor" at the level of individual components (a resistor and ideal capacitor)
and their behaviours, or at the more abstract level through general behaviour (\inv) and
using existential quantification (\texttt{exists}) to encapsulate all internal signals. 
Therefore capturing similarities between the differing levels of abstractions 
far outweigh their inevitable differences, making it possible to obtain a 
continuous process that ensures a direct mapping between a formal specification 
and its software solution.

>>>>

\subsection{Seamlessness and Reversibility}
\label{subsec:seamrever}
\emph{Seamlessness} is the use of a continuous process 
throughout the software lifecycle.
\emph{Reversibility} is the support for both forward and 
backward development process: from analysis to design 
and implementation, and back.
In VHDL-AMS, modelling represents an continious top-down-bottom-up
process. Top-down approach serves for design while bottom-up
serves for verification. The possibility of seamlessly translating 
changes made during a certain development phase back into earlier phases,
facilitates a stable and predictable environment and ensures the various 
models consistent with the code. Keeping in sync various models, documetation
and specification from forward progress to backward and redesign, preclude 
that design and implementation diverge to an inconsistent state. 
\emph{Seamlessness} also plays an important role in relating behaviours at
different levels of abstraction. For example, one may wish to analyze
a "real capacitor" at the level of individual components (a resistor and ideal capacitor)
and their behaviours, or at the more abstract level through general behaviour (\inv) and
using existential quantification (\texttt{exists}) to encapsulate all internal structure. 
Therefore capturing similarities between the differing levels of abstractions 
far outweigh their inevitable differences, making it possible to obtain a 
continuous process that ensures a direct mapping between a formal specification 
and its software solution.
